Is it fair? Searching for standards of fairness in the transportation justice literature

### 2024-05-14 Journal-manuscript/Journal-manuscript.qmd
Update to declaration

During the preparation of this work the authors used ChatGPT exclusively for copyediting: aiming to reduce word count, keep original style and correct typos. After using this tool, the authors reviewed and edited the content as needed and take full responsibility for the content of the publication.

>>>>

During the preparation of this work, the first and second authors used ChatGPT exclusively for copyediting in the "An appraisal of the lay of the land" section, aiming to reduce word count while keeping the original writing style and correct typos. After using this tool, all authors reviewed the manuscript and take full responsibility for the content of the publication.
